The Astropy Project

### 2017-12-10 main.tex
spell check. fixes #24

The \astropy project, as of the version 2.0 release, does not receive any direct
financial support for the development of \astropypkg.
Development of the software, all supporting materials, and community support are provided
by individuals who work on the \astropy project in their own personal
time, by individuals or groups contributing to \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgements.

@@

\section{Astropy Core Package version 2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
package
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to NaN in the original data
    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
    scipy's direct convolution (b), any pixel within range of the original NaN
    pixels is also set to NaN.  Panel (c) shows what happens if the NaNs are set
    to zero first: the originally NaN regions are depressed relative to their
    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
    where the missing pixels are replaced with values interpolated from their
    surroundings using the convolution kernel.
    \label{fig:convolution-example}
}
\end{figure}

>>>>

The \astropy project, as of the version 2.0 release, does not receive any direct
financial support for the development of \astropypkg.
Development of the software, all supporting materials, and community support are provided
by individuals who work on the \astropy project in their own personal
time, by individuals or groups contributing to \astropy as
part of a research project, or contributions from institutions that allocate
people to work on \astropy.
A list of organizations that have contributed to \astropy in this manner
can be found in the Acknowledgments.

@@

\section{Astropy Core Package version 2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
package
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the version 0.2 package.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the original data
    (a).  If the data are convolved with a Gaussian kernel on a $9\times 9$ grid using
    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the \texttt{NaN}s are set
    to zero first: the originally \texttt{NaN} regions are depressed relative to their
    surroundings.  Finally, panel (d) shows \astropypkg's convolution behavior,
    where the missing pixels are replaced with values interpolated from their
    surroundings using the convolution kernel.
    \label{fig:convolution-example}
}
\end{figure}
